---
title: "Democratic Erosion"
author: "Anthony Sutton"
date: "4/20/2022"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set arbitrary thresholds

```{r arbitrary_declarations}
dem_threshold = 0.5 #on vdem's 1-point scales
survival_threshold = 0.5 #as a probability
erosion_threshold = 1 #as multiple of standard deviations
treatment_threshold = 0.9 #percentile that distinguishes high clientelism/disinfo/polarization from low
                          #must hold high threshold else few democratic spells experience onset of "treatment"
                          # because they start the spell already above the threshold
lag_range = 10 #test time lags of dependent variables from 1 to this many years

#color scheme used in charts
dem_color = 'dodgerblue'
interlock_color = 'midnightblue'
client_color = 'sienna'
media_color = 'forestgreen'
disinfo_color = 'olivedrab3'
polar_color = 'tomato1'
```

# Load libraries
```{r libraries}
library(tidyverse)
library(scales) #for percent scales on charts
library(knitr)  #for kable function to format regression results
library(stargazer)  #for displaying multiple model results
library(MatchIt) #for matching analysis
```

# Load and shape data

This project uses V-Dem data:

Coppedge, Michael, John Gerring, Carl Henrik Knutsen, Staffan I. Lindberg, 
Jan Teorell, Nazifa Alizada, David Altman, et al. “V-Dem Dataset V11.1.” 
Varieties of Democracy Project, 2021. https://doi.org/10.23696/vdemds21.

Starting from the raw data file provided by V-Dem, this chunk trims the dataframe
to a manageable size. It need only be run once. Thereafter, the following code
will directly load the trimmed file.
)
```{r first_data}
##regime type data from V-Dem - one row per country year 
#vdem <- read_csv('./data/V-Dem-CY-Full+Others-v11.1.csv'

##trim to a manageable file size by selecting only relevant variables
#vdem <- vdem %>% select(country_name, country_text_id, year, COWcode,
#                        v2x_polyarchy, v2x_libdem, v2x_partipdem, v2x_delibdem, v2x_egaldem,
#                        v2xnp_client, v2elvotbuy, v2dlencmps, v2psprlnks, v2x_elecreg,
#                        v2smonex, v2smmefra, v2smgovdom, v2smpardom, v2smfordom, 
#                        v2cacamps, v2smpolsoc, v2smpolhate, v2psplats,
#                        e_migdpgro, e_migdppc,
#                        e_mipopula, e_miurbani,
#                        e_total_fuel_income_pc, e_total_resources_income_pc)

#write_csv(vdem, file = './data/vdem_trimmed.csv')
```

```{r subsequent_data}
vdem <- read_csv('./data/vdem_trimmed.csv')

vdem <- vdem %>% filter(!is.na(v2x_polyarchy))
```

Rescale variables to zero-to-one, and ensure 1 is the direction of
 more of that variable (not always more democratic)

```{r}
vdem$v2cacamps <- rescale(vdem$v2cacamps, to = c(0,1))
vdem$v2smpolsoc <- 1 - rescale(vdem$v2smpolsoc)
vdem$v2smpolhate <- 1 - rescale(vdem$v2smpolhate)
vdem$v2smonex <- rescale(vdem$v2smonex, to = c(0,1)) #already runs low to high
vdem$v2smmefra <- 1 - rescale(vdem$v2smmefra, to = c(0,1))
vdem$v2smgovdom <- 1 - rescale(vdem$v2smgovdom, to = c(0,1))
vdem$v2smpardom <- 1 - rescale(vdem$v2smpardom, to = c(0,1))
vdem$v2smfordom <- 1 - rescale(vdem$v2smfordom, to = c(0,1))
vdem$v2psprlnks <- 1 - rescale(vdem$v2psprlnks, to = c(0,1))
vdem$v2dlencmps <- 1 - rescale(vdem$v2dlencmps, to = c(0,1))
vdem$v2psplats <- 1 - rescale(vdem$v2psplats, to = c(0,1))
```

Count GDP per capita in thousands of dollars, changing from single dollars 
```{r}
vdem$e_migdppc <- vdem$e_migdppc / 1000
```

Recalculate natural resources income as fraction of gdp
```{r}
vdem$e_total_resources_percent <- 
  case_when(is.na(vdem$e_migdppc) ~ as.numeric(NA),
            vdem$e_migdppc <= 0 ~ as.numeric(NA),
            TRUE ~ vdem$e_total_resources_income_pc / vdem$e_migdppc )
```

Multiply variables to interact in linear regressions
 (needed to run linear models within a loop)
```{r}
vdem$clientXresources <- vdem$v2xnp_client * vdem$e_total_resources_percent #clientelism * natural resources
vdem$smmefraXsmpardom <- vdem$v2smmefra * vdem$v2smpardom #online fractionalization * party disinfo
vdem$smonexXsmmefra <- vdem$v2smonex * vdem$v2smmefra #online consumption * fractionalization
vdem$smonexXsmfordom <- vdem$v2smonex * vdem$v2smfordom #online consuption * foreign disinfo
vdem$smmefraXsmfordom <- vdem$v2smmefra * vdem$v2smfordom #online fractionalization * foreign disinfo
vdem$clientXcacamps <- vdem$v2cacamps * vdem$v2xnp_client #clientelism * political polarization
vdem$clientXsmpolsoc <- vdem$v2smpolsoc * vdem$v2xnp_client #clientelism * social polarization
vdem$smmefraXsmpolsoc <- vdem$v2smmefra * vdem$v2smpolsoc #online fractionalization * social polarization
```

Examine the data
```{r}
skimr::skim(vdem)
```

# Situate country-years within democratic spells

Label democratization and autocratization, which define spells

First, create empty variables
```{r}
vdem$democratize <- as.logical(NA)
vdem$autocratize <- as.logical(NA)
vdem$first_appear <- as.logical(FALSE)
```
 
Second, loop over every country-year
```{r}
for (i in seq_along(vdem$year)){
  #if no entry for the country in the prior year, label first year and skip to next country-year
  if (length(vdem$v2x_polyarchy[vdem$country_name == vdem$country_name[i] & vdem$year == (vdem$year[i] - 1)]) == 0) vdem$first_appear[i] <- TRUE
  if (vdem$first_appear[i] == TRUE) next
  
  #otherwise, identify the polyarchy score for the same country in the preceding year
  pre1_polyarchy <- vdem %>%
    filter(country_name == vdem$country_name[i] & year == (vdem$year[i] - 1)) %>%
    pull(v2x_polyarchy)
  
  #call it democratization if a country is a democracy this year and was not in prior year
  vdem$democratize[i] <- 
    case_when(pre1_polyarchy >= dem_threshold ~ FALSE,
              vdem$v2x_polyarchy[i] >= dem_threshold ~ TRUE,
              TRUE ~ FALSE
              )
  
  #call it autocratization if a country is an autocracy this year and was not in prior year
  vdem$autocratize[i] <- 
    case_when(pre1_polyarchy < dem_threshold ~ FALSE,
              vdem$v2x_polyarchy[i] < dem_threshold ~ TRUE,
              TRUE ~ FALSE
    )
}
```

Third, for countries first appearing in data, determine whether democratized 
 and view results
```{r}
vdem$democratize <- if_else(vdem$first_appear == TRUE,
                            if_else(vdem$v2x_polyarchy >= dem_threshold,
                                    TRUE,
                                    FALSE),
                            vdem$democratize)
summary(vdem$democratize)
```

Fourth, for countries first appearing in data, determine whether autocratized
 and view results
```{r}
vdem$autocratize <- if_else(vdem$first_appear == TRUE,
                            if_else(vdem$v2x_polyarchy < dem_threshold,
                                    TRUE,
                                    FALSE),
                            vdem$autocratize)
summary(vdem$autocratize)
```


Identify beginning of each democratic spell
```{r}
vdem$dem_spell_start <- as.numeric(NA)
 #loop over every country-year
for (i in seq_along(vdem$year)){
 #ignore autocracies
 if (vdem$v2x_polyarchy[i] < dem_threshold) next
 #recognize democratization years as their own spell starts
 if (vdem$democratize[i] == TRUE) vdem$dem_spell_start[i] <- vdem$year[i]
 if (vdem$democratize[i] == TRUE) next

 vdem$dem_spell_start[i] <- vdem %>%
   filter(country_name == vdem$country_name[i] &
            vdem$year < vdem$year[i] & 
            vdem$democratize == TRUE) %>%
   summarize(dem_spell_start = max(year)) %>%
   pull(dem_spell_start)
}

summary(vdem$dem_spell_start)
```

Name democratic spells
```{r}
vdem$dem_spell_name <- if_else(is.na(vdem$dem_spell_start),
                               as.character(NA),
                               paste(vdem$country_name, as.character(vdem$dem_spell_start)))
```

Check that every democratic country year is labeled with a spell start
```{r}
sum(!is.na(vdem$dem_spell_start)) == sum(vdem$v2x_polyarchy >= dem_threshold)
```

Identify prior peak polyarchy within same democratic spell
```{r}
vdem$dem_spell_peak = as.numeric(NA)
 ###loop over every country year
for (i in seq_along(vdem$year)){
  ###ignore autocracies
  if(is.na(vdem$dem_spell_start[i])) next
  ###examine polyarchy scores from each year during democratic spell, record highest
  vdem$dem_spell_peak[i] <- vdem %>% 
    filter(country_name == vdem$country_name[i] &
             year >= vdem$dem_spell_start[i] &
             year <= vdem$year[i]) %>% 
    summarize(peak_polyarchy = max(v2x_polyarchy), na.rm = TRUE) %>%
    pull(peak_polyarchy)
}
summary(vdem$dem_spell_peak)
```

Record running tally of length of democracy spell
```{r}
vdem$dem_spell_running <- vdem$year - vdem$dem_spell_start
```

Identify eventual outcome of each democracy spell
```{r}
vdem$dem_spell_outcome <- as.character(NA)

for (i in seq_along(vdem$year)){
vdem$dem_spell_outcome[i] <- 
  if_else(vdem$v2x_polyarchy[i] >= dem_threshold,
          if_else(sum(vdem$autocratize[vdem$country_name == vdem$country_name[i] & vdem$year >= vdem$year[i]]) > 0,
                  'autocracy',
                  'democracy'),
          as.character(NA))
}
vdem$dem_spell_outcome <- as.factor(vdem$dem_spell_outcome)

summary(vdem$dem_spell_outcome)
```

Note length of spells at autocratization or last year of data
```{r}
vdem <- vdem %>%
  group_by(dem_spell_name) %>%
  mutate(dem_spell_length = max(dem_spell_running)) %>%
  ungroup()
summary(vdem$dem_spell_length)
```

# Identify consolidated democracies

Count democracies as consolidated if their experience with democracy is 
 sufficiently long, high, and broad.

Chart outcomes by polyarchy height
```{r echo=FALSE}
vdem %>% filter(v2x_polyarchy >= dem_threshold) %>%
  group_by(polyarchy_cohort = round(v2x_polyarchy, digits = 2)) %>%
  mutate(outcome_rate = sum(dem_spell_outcome == 'democracy') / n()) %>%
  ggplot(aes(x = polyarchy_cohort, y = outcome_rate))+
  geom_point(size = 4, color = dem_color)+
  geom_smooth(method = 'loess', size = 2.5, color = dem_color)+
  coord_cartesian(ylim = c(0,1))+
  geom_hline(yintercept = 0.5, linetype = 'dashed')+
  geom_hline(yintercept = 0.8, linetype = 'dashed')+
  theme_minimal()+
  labs(title = 'Democracy Survival Rates',
       subtitle = '  by polyarchy height at year of observation',
       y = 'Survival Rate',
       x = 'V-Dem Polyarchy Score')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16)) 
ggsave(filename = "./visuals/democracy_survival_height.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

Calculate minimum polyarchy to predict survival above threshold
```{r}
height_threshold <- vdem %>% 
  filter(v2x_polyarchy >= dem_threshold) %>%
  group_by(polyarchy_cohort = round(v2x_polyarchy, digits = 2)) %>%
  summarize(outcome_rate = sum(dem_spell_outcome == 'democracy') / n()) %>%
  filter(outcome_rate < survival_threshold) %>%
  summarize(last_cohort = max(polyarchy_cohort)) %>%
  pull(last_cohort) + 0.01
height_threshold
```
Chart outcome by democracy spell length
```{r echo=FALSE}
vdem %>% 
  filter(v2x_polyarchy >= dem_threshold) %>%
  group_by(dem_spell_running) %>%
  mutate(outcome_rate = sum(dem_spell_outcome == 'democracy') / n()) %>%
  ggplot(aes(x = dem_spell_running, y = outcome_rate))+
  geom_point(size = 1.5, color = dem_color)+
  geom_smooth(method = 'loess', size = 2.5, color = dem_color)+
  coord_cartesian(ylim = c(0,1), xlim = c(0,110))+
  geom_hline(yintercept = 0.5, linetype = 'dashed')+
  geom_hline(yintercept = 0.8, linetype = 'dashed')+
  theme_minimal()+
  labs(title = 'Democracy Survival Rates',
       subtitle = '  by length of spell at year of observation',
       y = 'Survival Rate',
       x = 'Consecutive Years as Democracy (V-Dem Polyarchy)')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16)) 
ggsave(filename = "./visuals/democracy_survival_length.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

Calculate fraction of all democracy spells that lasted
```{r}
vdem %>% filter(dem_spell_running == 0) %>%
  summarize(count = n(), 
            stayed_democracies = sum(dem_spell_outcome == 'democracy'),
            survival_rate = stayed_democracies/count)
```

Calculate minimum spell length to predict survival above threshold
```{r}
length_threshold <- vdem %>% 
  filter(v2x_polyarchy >= dem_threshold) %>%
  group_by(dem_spell_running) %>%
  summarize(outcome_rate = sum(dem_spell_outcome == 'democracy') / n()) %>%
  filter(outcome_rate >= survival_threshold) %>%
  summarize(last_cohort = min(dem_spell_running)) %>%
  pull(last_cohort)
length_threshold
```

Compare vdem high level indexes
 Observe that the four other varieties of democracy
 tend to score lower than polyarchy
```{r}
vdem %>% filter(v2x_polyarchy >= dem_threshold) %>% 
  summarize(polyarchy = mean(v2x_polyarchy),
            liberal = mean(v2x_libdem, na.rm = TRUE),
            participatory = mean(v2x_partipdem, na.rm = TRUE),
            deliberative = mean(v2x_delibdem, na.rm = TRUE),
            egalitarian = mean(v2x_egaldem, na.rm = TRUE))
```

```{r ech=FALSE}
vdem %>% filter(v2x_polyarchy >= dem_threshold) %>%
  group_by(libdem_cohort = round(v2x_libdem, digits = 2)) %>%
  mutate(outcome_rate = sum(dem_spell_outcome == 'democracy') / n()) %>%
  ggplot(aes(x = libdem_cohort, y = outcome_rate))+
  geom_point(size = 4, color = dem_color)+
  geom_smooth(method = 'loess', size = 2.5, color = dem_color)+
  coord_cartesian(ylim = c(0,1))+
  geom_hline(yintercept = 0.5, linetype = 'dashed')+
  geom_hline(yintercept = 0.8, linetype = 'dashed')+
  theme_minimal()+
  labs(title = 'Democracy Survival Rates',
       subtitle = '  by liberal democracy at year of observation',
       y = 'Survival Rate',
       x = 'V-Dem Liberal Democracy Index')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16)) 
ggsave(filename = "./visuals/democracy_survival_libdem.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

```{r}
vdem %>% filter(v2x_polyarchy >= dem_threshold) %>%
  group_by(partipdem_cohort = round(v2x_partipdem, digits = 2)) %>%
  mutate(outcome_rate = sum(dem_spell_outcome == 'democracy') / n()) %>%
  ggplot(aes(x = partipdem_cohort, y = outcome_rate))+
  geom_point(size = 4, color = dem_color)+
  geom_smooth(method = 'loess', size = 2.5, color = dem_color)+
  coord_cartesian(ylim = c(0,1))+
  geom_hline(yintercept = 0.5, linetype = 'dashed')+
  geom_hline(yintercept = 0.8, linetype = 'dashed')+
  theme_minimal()+
  labs(title = 'Democracy Survival Rates',
       subtitle = '  by participatory democracy at year of observation',
       y = 'Survival Rate',
       x = 'V-Dem Participatory Democracy Index')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16)) 
ggsave(filename = "./visuals/democracy_survival_partipdem.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

```{r}
vdem %>% filter(v2x_polyarchy >= dem_threshold) %>%
  group_by(delibdem_cohort = round(v2x_delibdem, digits = 2)) %>%
  mutate(outcome_rate = sum(dem_spell_outcome == 'democracy') / n()) %>%
  ggplot(aes(x = delibdem_cohort, y = outcome_rate))+
  geom_point(size = 4, color = dem_color)+
  geom_smooth(method = 'loess', size = 2.5, color = dem_color)+
  coord_cartesian(ylim = c(0,1))+
  geom_hline(yintercept = 0.5, linetype = 'dashed')+
  geom_hline(yintercept = 0.8, linetype = 'dashed')+
  theme_minimal()+
  labs(title = 'Democracy Survival Rates',
       subtitle = '  by deliberative democracy at year of observation',
       y = 'Survival Rate',
       x = 'V-Dem Deliberative Democracy Index')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16)) 
ggsave(filename = "./visuals/democracy_survival_delibdem.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

```{r}
vdem %>% filter(v2x_polyarchy >= dem_threshold) %>%
  group_by(egaldem_cohort = round(v2x_egaldem, digits = 2)) %>%
  mutate(outcome_rate = sum(dem_spell_outcome == 'democracy') / n()) %>%
  ggplot(aes(x = egaldem_cohort, y = outcome_rate))+
  geom_point(size = 4, color = dem_color)+
  geom_smooth(method = 'loess', size = 2.5, color = dem_color)+
  coord_cartesian(ylim = c(0,1))+
  geom_hline(yintercept = 0.5, linetype = 'dashed')+
  geom_hline(yintercept = 0.8, linetype = 'dashed')+
  theme_minimal()+
  labs(title = 'Democracy Survival Rates',
       subtitle = '  by egalitarian democracy at year of observation',
       y = 'Survival Rate',
       x = 'V-Dem Egalitarian Democracy Index')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16)) 
ggsave(filename = "./visuals/democracy_survival_egaldem.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

Calculate survival rate for democracies scoring well on all indexes
```{r}
vdem %>% filter(v2x_polyarchy >= dem_threshold) %>%
  group_by(v2x_libdem >= dem_threshold &
             v2x_partipdem >= dem_threshold & 
             v2x_delibdem >= dem_threshold & 
             v2x_egaldem >= dem_threshold) %>%
  summarize(count = n(), 
            stayed_democracies = sum(dem_spell_outcome == 'democracy'),
            success_rate = stayed_democracies/count)
```
List all democratic spells that ever exceeded all thresholds in same year
```{r}
broad_dem_spell_list <- vdem %>% 
  filter(v2x_polyarchy >= dem_threshold,
         v2x_libdem >= dem_threshold &
           v2x_partipdem >= dem_threshold & 
           v2x_delibdem >= dem_threshold & 
           v2x_egaldem >= dem_threshold) %>%
  distinct(dem_spell_name) %>%
  pull(dem_spell_name)
```

Calculate survival rate predicted by whether broad democracy
```{r}
vdem %>% filter(v2x_polyarchy >= dem_threshold) %>%
  distinct(dem_spell_name, .keep_all = TRUE)  %>%
  group_by(broad_dem = dem_spell_name %in% broad_dem_spell_list) %>%
  summarize(stayed_democratic = sum(dem_spell_outcome == 'democracy'),
            count = n(),
            survival_rate = stayed_democratic / count)
```

Repeat process using individual thresholds predicting 80% survival
 Results are not very different - similar split of cases
```{r}
high_broad_dem_spell_list <- vdem %>% 
  filter(v2x_polyarchy >= 0.76,
         v2x_libdem >= 0.61 &
           v2x_partipdem >= 0.50 & 
           v2x_delibdem >= 0.59 & 
           v2x_egaldem >= 0.56) %>%
  distinct(dem_spell_name) %>%
  pull(dem_spell_name)

vdem %>% filter(v2x_polyarchy >= dem_threshold) %>%
  distinct(dem_spell_name, .keep_all = TRUE)  %>%
  group_by(high_broad_dem = dem_spell_name %in% high_broad_dem_spell_list) %>%
  summarize(stayed_democratic = sum(dem_spell_outcome == 'democracy'),
            count = n(),
            survival_rate = stayed_democratic / count)
```

Label each country-year as consolidated or not
 ...operationalizing consolidation by democracy spell length
```{r}
vdem$consolidated_long <- case_when(vdem$v2x_polyarchy < dem_threshold ~ as.logical(NA),
                                    vdem$dem_spell_running >= length_threshold ~ TRUE,
                                    TRUE ~ FALSE)
summary(vdem$consolidated_long)
```
 
 ...operationalizing consolidation by polyarchy height
```{r}
vdem$consolidated_high <- case_when(vdem$v2x_polyarchy < dem_threshold ~ as.logical(NA),
                                    vdem$v2x_polyarchy >= height_threshold ~ TRUE,
                                    TRUE ~ FALSE)
summary(vdem$consolidated_high)
```

 ...operationalizing consolidation by varietal breadth
```{r}
vdem$consolidated_broad <- case_when(vdem$v2x_polyarchy < dem_threshold ~ as.logical(NA),
                                     (vdem$v2x_libdem >= dem_threshold &
                                        vdem$v2x_partipdem >= dem_threshold & 
                                        vdem$v2x_delibdem >= dem_threshold & 
                                        vdem$v2x_egaldem >= dem_threshold) ~ TRUE,
                                     TRUE ~ FALSE)
summary(vdem$consolidated_broad)
```

Examine overlap among consolidation measures
```{r}
vdem %>% select(consolidated_long, consolidated_high, consolidated_broad) %>%
  na.omit() %>% 
  cor()
```
Create a variable for combined consolidation
```{r}
vdem$consolidated_lhb <- case_when(vdem$v2x_polyarchy < dem_threshold ~ as.logical(NA),
                                   (vdem$consolidated_long == TRUE &
                                      vdem$consolidated_high == TRUE &
                                      vdem$consolidated_broad == TRUE) ~ TRUE,
                                   TRUE ~ FALSE)
summary(vdem$consolidated_lhb)
```
Count democratic spells that ever consolidated
```{r}
vdem %>% filter(consolidated_lhb == TRUE) %>% 
  distinct(dem_spell_name) %>% 
  summarize(count = n())
```

Label erosion as any democratic country-year:
 *with polyarchy score at least X times 1 standard deviations below spell peak,
   where X is an arbitrarily defined multiple,
 *and so long as the spell ever peaked high enough to erode without autocratizing 
```{r}
vdem$erode <- case_when(vdem$v2x_polyarchy < dem_threshold ~ as.logical(NA),
                        vdem$dem_spell_peak < (dem_threshold + (erosion_threshold * sd(vdem$v2x_polyarchy[vdem$v2x_polyarchy >= dem_threshold]))) ~ as.logical(NA),
                        vdem$dem_spell_peak - vdem$v2x_polyarchy >= (erosion_threshold * sd(vdem$v2x_polyarchy[vdem$v2x_polyarchy >= dem_threshold])) ~ TRUE,
                        TRUE ~ FALSE)
summary(vdem$erode)
```
 
Count outcomes
```{r}
vdem %>% filter(erode == TRUE) %>%
  group_by(dem_spell_outcome) %>% 
  summarize(count = n())
```

Label all country-years within spell, saying whether spell included erosion
```{r}
vdem <- vdem %>% 
  group_by(dem_spell_name) %>%
  mutate(dem_spell_erosion = case_when(max(vdem$v2x_polyarchy, na.rm = TRUE) < dem_threshold ~ as.logical(NA),
                                       max(vdem$dem_spell_peak, na.rm = TRUE) < (erosion_threshold * sd(vdem$v2x_polyarchy[vdem$v2x_polyarchy >= dem_threshold])) ~ as.logical(NA),
                                       sum(erode, na.rm = TRUE) > 0 ~ TRUE,
                                       TRUE ~ FALSE)) %>%
  ungroup()
summary(vdem$dem_spell_erosion)
```

```{r}
vdem$dem_spell_outcome <- case_when(vdem$dem_spell_outcome == 'autocracy' ~ 'autocracy',
                                    vdem$dem_spell_erosion == TRUE ~ 'erosion',
                                    TRUE ~ as.character(vdem$dem_spell_outcome))
vdem$dem_spell_outcome <- as.factor(vdem$dem_spell_outcome)
summary(vdem$dem_spell_outcome)
```
Review available cases against which to build predictive models 
 Count and itemize consolidated democracies, by outcome
```{r}
vdem %>% 
  filter(consolidated_lhb == TRUE) %>% 
  group_by(dem_spell_outcome) %>%
  summarize(n_distinct(dem_spell_name))
```

```{r}
interlocked_list <-
vdem %>% 
  filter(consolidated_lhb == TRUE) %>% 
  group_by('Democratic Spell' = dem_spell_name) %>%
  summarize(Outcome = case_when(sum(dem_spell_outcome == 'autocracy') > 0 ~ 'autocratized',
                                sum(dem_spell_erosion == TRUE) > 0 ~ 'eroded',
                                TRUE ~ 'remained democratic')) %>%
  arrange('Democratic Spell') %>%
  print(n = 100)

write.table(interlocked_list, file = "./visuals/interlocked_list.txt", sep = ",", quote = FALSE, row.names = F)
```

Examine cases where consolidated regime autocratized
 Note that some (eg Denmark 1902) ended in foreign occupation
```{r}
vdem %>% filter(consolidated_lhb == TRUE, dem_spell_outcome == 'autocracy') %>% 
  distinct(dem_spell_name)
```

Examine cases where consolidated regime eroded but didn't autocratize
```{r}
vdem %>% filter(consolidated_lhb == TRUE, dem_spell_outcome == 'erosion') %>% 
  distinct(dem_spell_name)
```

Spin off data frames for all democratic country-years
 and for all country-years within democratic spells that ever consolidated
```{r}
vdem_dem = vdem %>% filter(v2x_polyarchy >= dem_threshold)
vdem <- vdem %>% 
  group_by(dem_spell_name) %>%
  mutate(ever_consolidated = if_else(sum(consolidated_lhb == TRUE, na.rm = TRUE) > 0,
                                     TRUE,
                                     FALSE)) %>%
  ungroup() 
vdem_con <- vdem %>%
  filter(ever_consolidated == TRUE)
```


# Summary statistics

Year range - full data set
```{r}
summary(vdem$year) 
```
first year with democracy
```{r}
vdem %>% filter(v2x_polyarchy >= dem_threshold) %>% summarize(min(year))
```
first year with consolidated democracy
```{r}
vdem %>% filter(consolidated_lhb == TRUE) %>% summarize(min(year))
```
Range for clientelism variable
```{r}
vdem %>% filter(!is.na(v2xnp_client)) %>% summarize(min(year), max(year), n_distinct(country_name))
```
Range for polarization variable
```{r}
vdem %>% filter(!is.na(v2cacamps)) %>% summarize(min(year), max(year), n_distinct(country_name))
```
Range for online usage and fractionalization measures
```{r}
vdem %>% filter(!is.na(smonexXsmmefra)) %>% summarize(min(year), max(year), n_distinct(country_name))
```
Range for party disinformation
```{r}
vdem %>% filter(!is.na(v2smpardom)) %>% summarize(min(year), max(year), n_distinct(country_name))
```

Identify number of regimes - total
```{r}
n_distinct(vdem$country_name)
```
Countries with any democratic spells
```{r}
vdem %>% filter(!is.na(dem_spell_name)) %>% summarize(n_distinct(country_name))
```
Unique democratic spells
```{r}
vdem %>% filter(!is.na(dem_spell_name)) %>% summarize(n_distinct(dem_spell_name))
```

Distribution of variables
```{r echo=FALSE}
ggplot(data = vdem, aes(x = v2x_polyarchy))+
  geom_histogram(bins = 20, fill = 'dodgerblue', color = 'white')+
  theme_minimal()+
  labs(title = 'Distribution of Democracy',
       subtitle = '  all countries, 1789-2020',
       y = '',
       x = 'V-Dem Polyarchy Score')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.text = element_text(size = 16),
        axis.text.y = element_blank()) 
ggsave(filename = "./visuals/democracy_histogram_all.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

```{r}
vdem %>% filter(v2x_polyarchy >= dem_threshold) %>%
ggplot(aes(x = v2x_polyarchy))+
  geom_histogram(bins = 20, fill = 'dodgerblue', color = 'white')+
  theme_minimal()+
  labs(title = 'Distribution of Democracy',
       subtitle = '  across democratic country-years',
       y = '',
       x = 'V-Dem Polyarchy Score')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.text = element_text(size = 16),
        axis.text.y = element_blank()) 
ggsave(filename = "./visuals/democracy_histogram_dems.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

```{r}
ggplot(data = (vdem %>% filter(consolidated_lhb == TRUE)), aes(x = v2x_polyarchy))+
  geom_histogram(bins = 20, fill = 'dodgerblue', color = 'white')+
  theme_minimal()+
  labs(title = 'Distribution of Democracy',
       subtitle = '  interlocked democracies, 1900-2020',
       y = '',
       x = 'V-Dem Polyarchy Score')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.text = element_text(size = 16),
        axis.text.y = element_blank()) 
ggsave(filename = "./visuals/democracy_histogram_interlocked.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

```{r}
ggplot(data = vdem, aes(x = year, y = v2x_polyarchy))+
  geom_point(aes(color = consolidated_lhb == TRUE, alpha = consolidated_lhb == TRUE))+
  scale_color_manual(values = c(dem_color, interlock_color), na.value = 'gray50')+ 
  scale_alpha_manual(values = c(0.1, 0.3), na.value = 0.06)+
  theme_minimal()+
  labs(title = 'Democracy over Time',
       #subtitle = '  noting interlocked democracies',
       x = '',
       y = 'V-Dem Polyarchy Score')+
  annotate('text', label = 'Democracies', color = dem_color, size = 7, x = 1825, y = 0.625)+
  annotate('text', label = 'Interlocked\nDemocracies', color = interlock_color, size = 7, x = 1860, y = 0.825)+
  theme(legend.position = 'none',
        title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16),
        axis.title.y = element_text(margin = margin(r = 8))) 
ggsave(filename = "./visuals/democracy_interlocked_over_time.jpg",
       width = 10,
       height = 6,
       units = 'in')

```

```{r}
vdem %>% 
  ggplot(aes(x = v2xnp_client))+
  geom_histogram(bins = 20, fill = client_color, color = 'white')+
  theme_minimal()+
  labs(title = 'Distribution of Clientelism',
       subtitle = '  across all country-years',
       y = '',
       x = 'V-Dem Clientelism Index')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.text = element_text(size = 16),
        axis.text.y = element_blank()) 
ggsave(filename = "./visuals/client_histogram.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

```{r}
vdem %>% 
  ggplot(aes(x = v2cacamps))+
  geom_histogram(bins = 20, fill = polar_color, color = 'white')+
  theme_minimal()+
  labs(title = 'Distribution of Polarization',
       subtitle = '  across all country-years',
       y = '',
       x = 'V-Dem Political Polarization Index')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.text = element_text(size = 16),
        axis.text.y = element_blank()) 
ggsave(filename = "./visuals/polar_histogram.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

```{r}
vdem %>% 
  ggplot(aes(x = smonexXsmmefra))+
  geom_histogram(bins = 20, fill = media_color, color = 'white')+
  theme_minimal()+
  labs(title = 'Distribution of Media Use and Fractionalization',
       subtitle = '  across all country-years',
       y = '',
       x = 'V-Dem Online Media Use X Fractionalization')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.text = element_text(size = 16),
        axis.text.y = element_blank()) 
ggsave(filename = "./visuals/media_histogram.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

```{r}
vdem %>% 
  filter(!is.na(smonexXsmmefra)) %>%
  group_by(year_factor = as.factor(year)) %>%
  summarize(avg_smonexXsmmefra = mean(smonexXsmmefra)) %>%
  ggplot(aes(x = year_factor, y = avg_smonexXsmmefra))+
  geom_point(size = 5, color = media_color)+
  theme_minimal()+
  scale_x_discrete(breaks = c(2000,2005,2010,2015,2020))+
  labs(title = 'Rise in Media Use and Fractionalization',
       subtitle = '  yearly averages across all countries',
       y = 'V-Dem Media Use  X Fractionalization',
       x = '')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16)) 
ggsave(filename = "./visuals/media_chronology.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

```{r}
vdem %>% 
  ggplot(aes(x = v2smpardom))+
  geom_histogram(bins = 20, fill = disinfo_color, color = 'white')+
  theme_minimal()+
  labs(title = 'Distribution of Party Disinformation',
       subtitle = '  across all country-years',
       y = '',
       x = 'V-Dem Index of Party Disinformation')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.text = element_text(size = 16),
        axis.text.y = element_blank()) 
ggsave(filename = "./visuals/par_disinfo_histogram.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

```{r}
vdem %>% 
  filter(!is.na(v2smpardom)) %>%
  group_by(year_factor = as.factor(year)) %>%
  summarize(avg_v2smpardom = mean(v2smpardom)) %>%
  ggplot(aes(x = year_factor, y = avg_v2smpardom))+
  geom_point(size = 5, color = disinfo_color)+
  theme_minimal()+
  scale_x_discrete(breaks = c(2000,2005,2010,2015,2020))+
  labs(title = 'Rise in Party Disinformation',
       subtitle = '  yearly averages across all countries',
       y = 'V-Dem Index of Party Disinformation',
       x = '')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16)) 
ggsave(filename = "./visuals/par_disinfo_chronology.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

```{r echo = FALSE, warning=FALSE}
vdem %>%
  filter(ever_consolidated == TRUE) %>% 
  group_by(dem_spell_name) %>% 
  summarize(age = max(dem_spell_length), outcome = (dem_spell_outcome)) %>% 
  ggplot(aes(x = age))+
  geom_histogram(aes(fill = outcome), binwidth = 20, color = 'white')
```

Demonstrate possibility of ephemeral spells when using a single threshold like 0.5
```{r}
vdem %>% filter(country_name == 'Albania', between(year, 2003, 2020)) %>%
  select(country_name, year, v2x_polyarchy) %>% 
  print(n = 20)
```

```{r}
vdem %>% filter(country_name == 'Kosovo', between(year, 2001, 2020)) %>%
  select(country_name, year, v2x_polyarchy) %>% 
  print(n = 20)
```
# Predict eventual autocratization or erosion

Produce a few illustrative statistics

Highest polyarchy peak that later autocratized
```{r}
vdem %>% 
  filter(dem_spell_outcome == 'autocracy') %>% 
  group_by(dem_spell_name) %>%
  summarize(farthest_faller = max(dem_spell_peak), last_year = max(year)) %>%
  arrange(desc(farthest_faller))
```

Distribution of lowest polyarchy scores after a country reached a high threshold

First identify mean and sd for all democratic country-years
```{r}
dems_polyarchy_mean <- vdem %>% 
  filter(v2x_polyarchy >= dem_threshold) %>%
  summarize(dems_polyarchy_mean = mean(v2x_polyarchy)) %>%
  pull(dems_polyarchy_mean)
dems_polyarchy_sd <- vdem %>% 
  filter(v2x_polyarchy >= dem_threshold) %>%
  summarize(dems_polyarchy_sd = sd(v2x_polyarchy)) %>%
  pull(dems_polyarchy_sd)
```

Then identify all democratic spells that ever exceeded 1 sd above democratic mean
```{r}
high_dems_reference_set <-
vdem %>%
  filter(v2x_polyarchy >= dems_polyarchy_mean + dems_polyarchy_sd) %>%
  group_by(country_name) %>%
  summarize(year_above_highthreshold = min(year))
```

Then log the lowest polyarchy score in a spell after it exceeded 1 sd above mean
```{r}
high_dems_reference_set$low_after_high <- as.numeric(NA)
for (i in seq_along(high_dems_reference_set$country_name)){
  high_dems_reference_set$low_after_high[i] <-
    vdem %>% filter(country_name == high_dems_reference_set$country_name[i] &
                    year >= high_dems_reference_set$year_above_highthreshold[i]) %>%
    summarize(low_after_high = min(v2x_polyarchy, na.rm = TRUE)) %>%
    pull(low_after_high)
}
```

Identify lowest sinking democracies that previously exceeded 1 sd above mean
```{r}
high_dems_reference_set %>% arrange(low_after_high)
```

```{r}
count(high_dems_reference_set, autocratized_after_high_threshold = low_after_high < dem_threshold)
```

```{r}
count(high_dems_reference_set, fell_below_avg_dem_after_high_threshold = low_after_high < dems_polyarchy_mean)
```

Chart distribution of lowest polyarchy scores after exceeding 1 sd above mean
```{r echo = FALSE}
ggplot(data = high_dems_reference_set, aes(x = low_after_high))+
  geom_histogram(binwidth = 0.05)+
  geom_vline(xintercept = dems_polyarchy_mean)+
  geom_vline(xintercept = dems_polyarchy_mean + dems_polyarchy_sd, linetype = 'dashed')
```
Examine independent variables

clientelism
```{r}
summary(vdem$v2xnp_client) #clientelism index, rolls up psprlnks and dlencmps plus additional variables
```
```{r}
summary(vdem$v2psprlnks) #how parties link to constituents
```
```{r}
summary(vdem$v2dlencmps) #particularistic social spending
```
 mutual correlations
```{r}
vdem %>% select(v2xnp_client, v2psprlnks, v2dlencmps) %>%
  na.omit() %>% 
  cor()
```
information control
```{r}
summary(vdem$v2smonex) # online media consumption
```
```{r}
summary(vdem$v2smmefra) # online media fractionalization
```
```{r}
summary(vdem$v2smgovdom) # government disseminates false info
```
```{r}
summary(vdem$v2smpardom) # party disseminates false info
```
```{r}
summary(vdem$v2smfordom) # foreign governments inject false info
```
 mutual correlations
```{r}
vdem %>% select(v2smonex, v2smmefra, v2smgovdom, v2smpardom, v2smfordom) %>%
  na.omit() %>% 
  cor()
```

polarization
```{r}
summary(vdem$v2cacamps) # political polarization extends into society
```
```{r}
summary(vdem$v2smpolsoc) # societal polarization
```
```{r}
summary(vdem$v2smpolhate) # parties use hate speech
```
 mutual correlations
```{r}
vdem %>% select(v2cacamps, v2smpolsoc, v2smpolhate) %>%
  na.omit() %>% 
  cor()
```

# Model to correlate corrosive factors to reductions in democracy
nomenclature 
*m1 = all democratic cases, predict autocratization
*m2 = consolidated cases, predict autocratization
*m3 = all democratic cases, predict erosion
*m4 = consolidated cases, predict erosion
*m5 = consolidated cases, predict autocratization using matching for controls
*m6 = consolidated cases, predict erosion using matching for controls
*m7 = consolidated cases, predict [autocratization or erosion]
*m8 = consolidated cases, predict [autocratization or erosion] using matching

Whenever matches are made as control groups, plots show the propensity distribution,
 which suggests whether matches are good.

model clientelism
```{r}
cm1 <- lm(dem_spell_outcome == 'autocracy' ~ v2xnp_client + v2x_polyarchy + e_migdppc + as.factor(year), data = vdem_dem)
cm2 <- lm(dem_spell_outcome == 'autocracy' ~ v2xnp_client + v2x_polyarchy + e_migdppc + as.factor(year), data = vdem_con)
cm3 <- lm(dem_spell_erosion == TRUE ~ v2xnp_client + v2x_polyarchy + e_migdppc + as.factor(year), data = vdem_dem)
cm4 <- lm(dem_spell_erosion == TRUE ~ v2xnp_client + v2x_polyarchy + e_migdppc + as.factor(year), data = vdem_con)
```

```{r}
match_client <- matchit(v2xnp_client >= mean(vdem_con$v2xnp_client, na.rm = TRUE) ~ 
                          v2x_polyarchy + e_migdppc + as.factor(year), 
                        data = vdem_con %>% filter(!is.na(v2x_polyarchy), !is.na(e_migdppc)),
                        method = 'nearest', distance = 'glm')
plot(match_client, type = "jitter", interactive = FALSE)
```
```{r}
vdem_client <- match.data(match_client)
cm5 <- lm(dem_spell_outcome == 'autocracy' ~ v2xnp_client + v2x_polyarchy + e_migdppc + as.factor(year), 
          data = vdem_client, 
          weights = weights)

cm6 <- lm(dem_spell_erosion == TRUE ~ v2xnp_client + v2x_polyarchy + e_migdppc + as.factor(year), 
          data = vdem_client, 
          weights = weights)

cm7 <- lm(dem_spell_outcome != 'democracy' ~ v2xnp_client + v2x_polyarchy + e_migdppc + as.factor(year), data = vdem_con)

cm8 <- lm(dem_spell_outcome != 'democracy' ~ v2xnp_client + v2x_polyarchy + e_migdppc + as.factor(year), 
          data = vdem_client, 
          weights = weights)
```

model media
```{r}
mm1_full <- lm(dem_spell_outcome == 'autocracy' ~ v2smonex + v2smmefra + v2smgovdom + v2smpardom + v2smfordom + v2x_polyarchy + e_migdppc + as.factor(year), data = vdem_dem)

mm2_full <- lm(dem_spell_outcome == 'autocracy' ~ v2smonex + v2smmefra + v2smgovdom + v2smpardom + v2smfordom + v2x_polyarchy + e_migdppc + as.factor(year), data = vdem_con)

mm3_full <- lm(dem_spell_erosion == TRUE ~ v2smonex + v2smmefra + v2smgovdom + v2smpardom + v2smfordom + v2x_polyarchy + e_migdppc + as.factor(year), data = vdem_dem)

mm4_full <- lm(dem_spell_erosion == TRUE ~ v2smonex + v2smmefra + v2smgovdom + v2smpardom + v2smfordom + v2x_polyarchy + e_migdppc + as.factor(year), data = vdem_con)

mm7_full <- lm(dem_spell_outcome != 'democracy' ~ v2smonex + v2smmefra + v2smgovdom + v2smpardom + v2smfordom + v2x_polyarchy + e_migdppc + as.factor(year), data = vdem_con)
```

```{r}
match_consume <- matchit(v2smonex >= mean(vdem_con$v2smonex, na.rm = TRUE) ~ 
                           v2x_polyarchy + e_migdppc + as.factor(year), 
                         data = vdem_con %>% filter(!is.na(v2smonex), !is.na(v2x_polyarchy), !is.na(e_migdppc)),
                         method = 'nearest', distance = 'glm')
plot(match_consume, type = "jitter", interactive = FALSE)
```

```{r}
vdem_consume <- match.data(match_consume)
mm5_consume <- lm(dem_spell_outcome == 'autocracy' ~ v2smonex + v2x_polyarchy + e_migdppc + as.factor(year), 
                  data = vdem_consume, 
                  weights = weights)

mm8_consume <- lm(dem_spell_outcome != 'democracy' ~ v2smonex + v2x_polyarchy + e_migdppc + as.factor(year), 
                  data = vdem_consume, 
                  weights = weights)
```

```{r}
match_fraction <- matchit(v2smmefra >= mean(vdem_con$v2smmefra, na.rm = TRUE) ~ 
                            v2x_polyarchy + e_migdppc + as.factor(year), 
                          data = vdem_con %>% filter(!is.na(v2smmefra), !is.na(v2x_polyarchy), !is.na(e_migdppc)),
                          method = 'nearest', distance = 'glm')
plot(match_fraction, type = "jitter", interactive = FALSE)
```

```{r}
vdem_fraction <- match.data(match_fraction)
mm5_fraction <- lm(dem_spell_outcome == 'autocracy' ~ v2smmefra + v2x_polyarchy + e_migdppc + as.factor(year), 
                   data = vdem_fraction, 
                   weights = weights)

mm8_fraction <- lm(dem_spell_outcome != 'democracy' ~ v2smmefra + v2x_polyarchy + e_migdppc + as.factor(year), 
                   data = vdem_fraction, 
                   weights = weights)
```

```{r}
match_gov_disinfo <- matchit(v2smgovdom >= mean(vdem_con$v2smgovdom, na.rm = TRUE) ~ 
                               v2x_polyarchy + e_migdppc + as.factor(year), 
                             data = vdem_con %>% filter(!is.na(v2smgovdom), !is.na(v2x_polyarchy), !is.na(e_migdppc)),
                             method = 'nearest', distance = 'glm')
plot(match_gov_disinfo, type = "jitter", interactive = FALSE)
```

```{r}
vdem_gov_disinfo <- match.data(match_gov_disinfo)
mm5_gov <- lm(dem_spell_outcome == 'autocracy' ~ v2smgovdom + v2x_polyarchy + e_migdppc + as.factor(year), 
              data = vdem_gov_disinfo, 
              weights = weights)

mm8_gov <- lm(dem_spell_outcome != 'democracy' ~ v2smgovdom + v2x_polyarchy + e_migdppc + as.factor(year), 
              data = vdem_gov_disinfo, 
              weights = weights)
```

```{r}
match_par_disinfo <- matchit(v2smpardom >= mean(vdem_con$v2smpardom, na.rm = TRUE) ~ 
                               v2x_polyarchy + e_migdppc + as.factor(year), 
                             data = vdem_con %>% filter(!is.na(v2smpardom), !is.na(v2x_polyarchy), !is.na(e_migdppc)),
                             method = 'nearest', distance = 'glm')
plot(match_par_disinfo, type = "jitter", interactive = FALSE)
```

```{r}
vdem_par_disinfo <- match.data(match_par_disinfo)
mm5_par <- lm(dem_spell_outcome == 'autocracy' ~ v2smpardom + v2x_polyarchy + e_migdppc + as.factor(year), 
              data = vdem_gov_disinfo, 
              weights = weights)

mm8_par <- lm(dem_spell_outcome != 'democracy' ~ v2smpardom + v2x_polyarchy + e_migdppc + as.factor(year), 
              data = vdem_gov_disinfo, 
              weights = weights)
```

```{r}

match_for_disinfo <- matchit(v2smfordom >= mean(vdem_con$v2smfordom, na.rm = TRUE) ~ 
                               v2x_polyarchy + e_migdppc + as.factor(year), 
                             data = vdem_con %>% filter(!is.na(v2smfordom), !is.na(v2x_polyarchy), !is.na(e_migdppc)),
                             method = 'nearest', distance = 'glm')
plot(match_for_disinfo, type = "jitter", interactive = FALSE)
```

```{r}
vdem_for_disinfo <- match.data(match_for_disinfo)
mm5_for <- lm(dem_spell_outcome == 'autocracy' ~ v2smfordom + v2x_polyarchy + e_migdppc + as.factor(year), 
              data = vdem_for_disinfo, 
              weights = weights)

mm8_for <- lm(dem_spell_outcome != 'democracy' ~ v2smfordom + v2x_polyarchy + e_migdppc + as.factor(year), 
              data = vdem_for_disinfo, 
              weights = weights)
```

model polarization
```{r}
pm1_full <- lm(dem_spell_outcome == 'autocracy' ~ v2cacamps + v2smpolsoc + v2smpolhate + v2x_polyarchy + e_migdppc + as.factor(year), data = vdem_dem)

pm2_full <- lm(dem_spell_outcome == 'autocracy' ~ v2cacamps + v2smpolsoc + v2smpolhate + v2x_polyarchy + e_migdppc + as.factor(year), data = vdem_con)

pm3_full <- lm(dem_spell_erosion == TRUE ~ v2cacamps + v2smpolsoc + v2smpolhate + v2x_polyarchy + e_migdppc + as.factor(year), data = vdem_dem)

pm4_full <- lm(dem_spell_erosion == TRUE ~ v2cacamps + v2smpolsoc + v2smpolhate + v2x_polyarchy + e_migdppc + as.factor(year), data = vdem_con)

pm7_full <- lm(dem_spell_outcome != 'democracy' ~ v2cacamps + v2smpolsoc + v2smpolhate + v2x_polyarchy + e_migdppc + as.factor(year), data = vdem_con)
```

# Search for most telling time lag
Write custom function 
to find optimal time lag for regression on any set of variables
```{r}
test_lags <- function(df = vdem, vars) {
  model_results <- data.frame(time_lag = c(1:lag_range),
                              regression_coef = as.numeric(NA),
                              p_value = as.numeric(NA))
  
  for (i in 1:lag_range){
    wdf <- df %>%
      group_by(country_name) %>%
      arrange(year) %>%
      mutate(v2x_polyarchy_lagged = lead(v2x_polyarchy, n = i)) %>%
      ungroup()
    wdf$polyarchy_change <- wdf$v2x_polyarchy_lagged - wdf$v2x_polyarchy
    wdf$year_factor <- as.factor(wdf$year)
    wdf <- wdf %>% filter(consolidated_lhb == TRUE)
    
    wm <- lm(polyarchy_change ~ ., data = wdf[,c('polyarchy_change', vars, 'year_factor')])
    model_results$regression_coef[i] <- summary(wm)$coefficients[2,'Estimate'] #coefficient
    model_results$p_value[i] <- summary(wm)$coefficients[2, 4] #p-value
  }
  print(model_results)
  print(model_results[model_results %>%
                        filter(p_value < 0.05) %>%
                        summarize(strongest_prediction = time_lag[which.max(abs(regression_coef))]) %>%
                        pull(strongest_prediction),])
}
```

Find lag length that provides most powerful predictions

```{r}
test_lags(vars = c('v2xnp_client', 'v2x_polyarchy', 'e_migdppc'))
```
```{r}
test_lags(vars = c('v2xnp_client', 'v2x_polyarchy', 'e_migdppc', 'e_total_resources_percent'))
```
```{r}
test_lags(vars = c('v2smonex', 'v2x_polyarchy', 'e_migdppc'))
```
```{r}
test_lags(vars = c('v2smmefra', 'v2x_polyarchy', 'e_migdppc'))
```
```{r}
test_lags(vars = c('v2smgovdom', 'v2x_polyarchy', 'e_migdppc'))
```
```{r}
test_lags(vars = c('v2smpardom', 'v2x_polyarchy', 'e_migdppc'))
```
```{r}
test_lags(vars = c('v2smfordom', 'v2x_polyarchy', 'e_migdppc'))
```
```{r}
test_lags(vars = c('v2cacamps', 'v2x_polyarchy', 'e_migdppc'))
```
```{r}
test_lags(vars = c('v2smpolsoc', 'v2x_polyarchy', 'e_migdppc'))
```
```{r}
test_lags(vars = c('v2smpolhate', 'v2x_polyarchy', 'e_migdppc'))
```

Find optimal lag for models with interacted variables
```{r}
test_lags(vars = c('smmefraXsmpardom', 'v2smmefra', 'v2smpardom', 'v2x_polyarchy', 'e_migdppc'))
```
```{r}
test_lags(vars = c('smonexXsmmefra', 'v2smonex', 'v2smmefra', 'v2x_polyarchy', 'e_migdppc'))
```
```{r}
test_lags(vars = c('smonexXsmfordom', 'v2smonex', 'v2smfordom', 'v2x_polyarchy', 'e_migdppc'))
```
```{r}
test_lags(vars = c('smmefraXsmfordom', 'v2smmefra', 'v2smfordom', 'v2x_polyarchy', 'e_migdppc'))
```
```{r}
test_lags(vars = c('clientXsmpolsoc', 'v2xnp_client', 'v2smpolsoc', 'v2x_polyarchy', 'e_migdppc'))
```
```{r}
test_lags(vars = c('smmefraXsmpolsoc', 'v2smmefra', 'v2smpolsoc', 'v2x_polyarchy', 'e_migdppc'))
```
```{r}
test_lags(vars = c('clientXresources', 'v2xnp_client', 'e_total_resources_percent', 'v2x_polyarchy', 'e_migdppc'))
```
```{r}
test_lags(vars = c('clientXcacamps', 'v2xnp_client', 'v2cacamps', 'v2x_polyarchy', 'e_migdppc'))
```

Run models at best time lag of 10 years, and export results

Record change in polyarchy scores over 10 years
```{r}
vdem <- vdem %>% 
  group_by(country_name) %>%
  arrange(year) %>%
  mutate(v2x_polyarchy_lagged = lead(v2x_polyarchy, n = 10)) %>%
  ungroup()
vdem$polyarchy_change <- vdem$v2x_polyarchy_lagged - vdem$v2x_polyarchy

```

```{r}
cm_print <- lm(polyarchy_change ~ v2xnp_client + v2x_polyarchy + e_migdppc + as.factor(year), 
               data = (vdem %>% filter(consolidated_lhb == TRUE)))
summary(cm_print)
```

```{r}
pm_print <- lm(polyarchy_change ~ v2cacamps + v2x_polyarchy + e_migdppc + as.factor(year), 
               data = (vdem %>% filter(consolidated_lhb == TRUE)))
summary(pm_print)
```

```{r}
mm_print <- lm(polyarchy_change ~ (v2smonex * v2smmefra) + v2x_polyarchy + e_migdppc + as.factor(year), 
               data = (vdem %>% filter(consolidated_lhb == TRUE)))
summary(mm_print)
```

```{r}
dm_print <- lm(polyarchy_change ~ v2smpardom + v2x_polyarchy + e_migdppc + as.factor(year), 
               data = (vdem %>% filter(consolidated_lhb == TRUE)))
summary(dm_print)
```

```{r}
fullm_print <- lm(polyarchy_change ~ v2xnp_client + v2cacamps + (v2smonex * v2smmefra) + v2smpardom + v2x_polyarchy + e_migdppc + as.factor(year), 
                  data = (vdem %>% filter(consolidated_lhb == TRUE)))
summary(fullm_print)
```

```{r}
threem_print <- lm(polyarchy_change ~ v2xnp_client + v2cacamps + v2smpardom + v2x_polyarchy + e_migdppc + as.factor(year), 
                         data = (vdem %>% filter(consolidated_lhb == TRUE)))
summary(threem_print)
```

Save out model results
```{r}
stargazer(cm_print, pm_print, mm_print, dm_print, fullm_print, 
          title = 'Solvents of Democracy',
          keep = c('polyarchy_change', 'v2xnp_client', 'v2cacamps', 'v2smonex', 'v2smmefra', 'v2smpardom',
                   'v2x_polyarchy', 'e_migdppc'),
          dep.var.labels = 'Change in Polyarchy Score After 10 Years',
          model.names = TRUE,
          covariate.labels = c('Clientelism', 'Polarization', 'Online Media Consumption', 'Online Media Fractionalization', 'Party Disinformation',
                               'Level of Democracy', 'GDP Per Capita', 'Online Media Consumption X Fractionalization'),
          nobs = TRUE,
          type = 'html',
          out = './models/democracy_erosion_model_results.doc')

stargazer(cm_print, pm_print, dm_print, threem_print, 
          title = 'Solvents of Democracy',
          keep = c('polyarchy_change', 'v2xnp_client', 'v2cacamps', 'v2smpardom',
                   'v2x_polyarchy', 'e_migdppc'),
          dep.var.labels = 'Change in Polyarchy Score After 10 Years',
          model.names = TRUE,
          covariate.labels = c('Clientelism', 'Polarization', 'Party Disinformation',
                               'Level of Democracy', 'GDP Per Capita'),
          nobs = TRUE,
          type = 'html',
          out = './models/corrosive_factors_model_results.doc')
```

Chart interacted variables

Preliminary terms
```{r}
lag_years = 10
point_scale = seq(from = 0, to = 1, by = 0.05)
df = vdem_con
```

Chart party disinformation by media fractionalization
```{r}
mimir <- data.frame(v2smpardom = rep(point_scale, times = length(point_scale)),
                    v2smmefra = rep(point_scale, each = length(point_scale)),
                    v2x_polyarchy = median(vdem_con$v2x_polyarchy[df$v2x_polyarchy >= 0.5], na.rm = TRUE),
                    e_migdppc = median(vdem_con$e_migdppc[df$v2x_polyarchy >= 0.5], na.rm = TRUE))
wdf <- vdem %>%
  group_by(country_name) %>%
  arrange(year) %>%
  mutate(v2x_polyarchy_lagged = lead(v2x_polyarchy, n = lag_years)) %>%
  ungroup()%>%
  filter(consolidated_lhb == TRUE)
wdf$polyarchy_change <- wdf$v2x_polyarchy_lagged - wdf$v2x_polyarchy
wm <- lm(polyarchy_change ~ v2smpardom * v2smmefra + v2x_polyarchy + e_migdppc, data = wdf)

mimir <- mimir %>% mutate(expected_polyarchy = predict(object = wm, newdata = mimir))
mimir %>% filter(v2smmefra %in% c(0.25, 0.75)) %>%
ggplot(aes(x = v2smpardom, y = expected_polyarchy, color = as.factor(v2smmefra)))+
  geom_line(size = 2.5)+
  scale_color_manual(values = c(disinfo_color, polar_color),
                     labels = c('low', 'high'))+
  theme_minimal()+
  labs(title = 'Party Disinformation X Fractionalization',
       subtitle = '  affect democracy 10 years later',
       y = 'Predicted Polyarchy Change',
       x = 'Party Disinformation',
       color = 'Fractionalization')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        axis.title.y = element_text(margin = margin(r = 8)),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16),
        legend.title = element_text(size = 18),
        legend.text = element_text(size = 16))
ggsave(filename = "./visuals/model_pardisinfo_fract_inter.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

Repeat chart with internal labels
```{r}
mimir %>% filter(v2smmefra %in% c(0.25, 0.75)) %>%
  ggplot(aes(x = v2smpardom, y = expected_polyarchy, color = as.factor(v2smmefra)))+
  geom_line(size = 2.5)+
  scale_color_manual(values = c(disinfo_color, polar_color),
                     labels = c('low', 'high'))+
  theme_minimal()+
  labs(title = 'Party Disinformation X Fractionalization',
       subtitle = '  affect democracy 10 years later',
       y = 'Predicted Polyarchy Change',
       x = 'Party Disinformation',
       color = 'Fractionalization')+
  annotate('text', label = 'low fractionalization', size = 8, color = disinfo_color, x = 0.75, y = -0.0125)+
  annotate('text', label = 'high fractionalization', size = 8, color = polar_color, x = 0.25, y = -0.0625)+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        axis.title.y = element_text(margin = margin(r = 8)),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16),
        legend.position = 'none')
ggsave(filename = "./visuals/model_pardisinfo_fract_inter_nolegend.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

Chart online consumption by media fractionalization
```{r}
mimir <- data.frame(v2smonex = rep(point_scale, times = length(point_scale)),
                    v2smmefra = rep(point_scale, each = length(point_scale)),
                    v2x_polyarchy = median(vdem_con$v2x_polyarchy[df$v2x_polyarchy >= 0.5], na.rm = TRUE),
                    e_migdppc = median(vdem_con$e_migdppc[df$v2x_polyarchy >= 0.5], na.rm = TRUE),
                    year = as.factor(2010))
wdf <- vdem %>%
  group_by(country_name) %>%
  arrange(year) %>%
  mutate(v2x_polyarchy_lagged = lead(v2x_polyarchy, n = lag_years)) %>%
  ungroup() %>%
  filter(consolidated_lhb == TRUE)
wdf$polyarchy_change <- wdf$v2x_polyarchy_lagged - wdf$v2x_polyarchy
wm <- lm(polyarchy_change ~ v2smonex * v2smmefra + v2x_polyarchy + e_migdppc + as.factor(year), data = wdf)

mimir <- mimir %>% mutate(expected_polyarchy = predict(object = wm, newdata = mimir))
mimir %>% filter(v2smmefra %in% c(0.25, 0.75)) %>%
  ggplot(aes(x = v2smonex, y = expected_polyarchy, color = as.factor(v2smmefra)))+
  geom_line(size = 2.5)+
  scale_color_manual(guide = 'none', 
                     values = c(media_color, disinfo_color))+
  theme_minimal()+
  labs(title = 'Online Use X Fractionalization',
       subtitle = '  affect democracy 10 years later',
       y = 'Predicted Polyarchy Change',
       x = 'Online Media Consumption')+
  annotate('text', label = 'at low fractionalization', color = media_color, size = 7, x = 0.25, y = -0.04)+
  annotate('text', label = 'at high fractionalization', color = disinfo_color, size = 7, x = 0.66, y = -0.125)+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        axis.title.y = element_text(margin = margin(r = 8)),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16),
        legend.position = 'none') 
ggsave(filename = "./visuals/model_online_fract_inter.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

Chart online consumption by foreign disinformation
```{r}

mimir <- data.frame(v2smonex = rep(point_scale, times = length(point_scale)),
                    v2smfordom = rep(point_scale, each = length(point_scale)),
                    v2x_polyarchy = median(vdem_con$v2x_polyarchy[df$v2x_polyarchy >= 0.5], na.rm = TRUE),
                    e_migdppc = median(vdem_con$e_migdppc[df$v2x_polyarchy >= 0.5], na.rm = TRUE))
wdf <- vdem %>%
  group_by(country_name) %>%
  arrange(year) %>%
  mutate(v2x_polyarchy_lagged = lead(v2x_polyarchy, n = lag_years)) %>%
  ungroup()%>%
  filter(consolidated_lhb == TRUE)
wdf$polyarchy_change <- wdf$v2x_polyarchy_lagged - wdf$v2x_polyarchy
wm <- lm(polyarchy_change ~ v2smonex * v2smfordom + v2x_polyarchy + e_migdppc, data = wdf)

mimir <- mimir %>% mutate(expected_polyarchy = predict(object = wm, newdata = mimir))
mimir %>% filter(v2smfordom %in% c(0.25, 0.75)) %>%
  ggplot(aes(x = v2smonex, y = expected_polyarchy, color = as.factor(v2smfordom)))+
  geom_line(size = 2.5)+
  scale_color_manual(values = c(media_color, disinfo_color),
                     labels = c('low', 'high'))+
  theme_minimal()+
  labs(title = 'Online Consumption X Foreign Disinformation',
       subtitle = '  affect democracy 10 years later',
       y = 'Predicted Polyarchy Change',
       x = 'Online Consumption',
       color = 'Foreign\n Disinfo')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        axis.title.y = element_text(margin = margin(r = 8)),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16),
        legend.title = element_text(size = 18),
        legend.text = element_text(size = 16))
ggsave(filename = "./visuals/model_online_fordisinfo_inter.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

Chart foreign disinformation by media fractionalization
```{r}
mimir <- data.frame(v2smfordom = rep(point_scale, times = length(point_scale)),
                    v2smmefra = rep(point_scale, each = length(point_scale)),
                    v2x_polyarchy = median(vdem_con$v2x_polyarchy[df$v2x_polyarchy >= 0.5], na.rm = TRUE),
                    e_migdppc = median(vdem_con$e_migdppc[df$v2x_polyarchy >= 0.5], na.rm = TRUE))
wdf <- vdem %>%
  group_by(country_name) %>%
  arrange(year) %>%
  mutate(v2x_polyarchy_lagged = lead(v2x_polyarchy, n = lag_years)) %>%
  ungroup()%>%
  filter(consolidated_lhb == TRUE)
wdf$polyarchy_change <- wdf$v2x_polyarchy_lagged - wdf$v2x_polyarchy
wm <- lm(polyarchy_change ~ v2smfordom * v2smmefra + v2x_polyarchy + e_migdppc, data = wdf)

mimir <- mimir %>% mutate(expected_polyarchy = predict(object = wm, newdata = mimir))
mimir %>% filter(v2smmefra %in% c(0.25, 0.75)) %>%
  ggplot(aes(x = v2smfordom, y = expected_polyarchy, color = as.factor(v2smmefra)))+
  geom_line(size = 2.5)+
  scale_color_manual(values = c(disinfo_color, polar_color),
                     labels = c('low', 'high'))+
  theme_minimal()+
  labs(title = 'Foreign Disinformation X Fractionalization',
       subtitle = '  affect democracy 10 years later',
       y = 'Predicted Polyarchy Change',
       x = 'Foreign Disinformation',
       color = 'Fractionalization')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        axis.title.y = element_text(margin = margin(r = 8)),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16),
        legend.title = element_text(size = 18),
        legend.text = element_text(size = 16))
ggsave(filename = "./visuals/model_fordisinfo_fract_inter.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

Repeat with internal lables
```{r}
mimir %>% filter(v2smmefra %in% c(0.25, 0.75)) %>%
  ggplot(aes(x = v2smfordom, y = expected_polyarchy, color = as.factor(v2smmefra)))+
  geom_line(size = 2.5)+
  scale_color_manual(values = c(disinfo_color, polar_color),
                     labels = c('low', 'high'))+
  theme_minimal()+
  labs(title = 'Foreign Disinformation X Fractionalization',
       subtitle = '  affect democracy 10 years later',
       y = 'Predicted Polyarchy Change',
       x = 'Foreign Disinformation',
       color = 'Fractionalization')+
  annotate('text', label = 'low fractionalization', size = 8, color = disinfo_color, x = 0.5, y = -0.01)+
  annotate('text', label = 'high fractionalization', size = 8, color = polar_color, x = 0.4, y = -0.05)+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        axis.title.y = element_text(margin = margin(r = 8)),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16),
        legend.position = 'none')
ggsave(filename = "./visuals/model_fordisinfo_fract_inter_nolegend.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

Chart clientelism by polarized society
```{r}
mimir <- data.frame(v2xnp_client = rep(point_scale, times = length(point_scale)),
                    v2smpolsoc = rep(point_scale, each = length(point_scale)),
                    v2x_polyarchy = median(vdem_con$v2x_polyarchy[df$v2x_polyarchy >= 0.5], na.rm = TRUE),
                    e_migdppc = median(vdem_con$e_migdppc[df$v2x_polyarchy >= 0.5], na.rm = TRUE))
wdf <- vdem %>%
  group_by(country_name) %>%
  arrange(year) %>%
  mutate(v2x_polyarchy_lagged = lead(v2x_polyarchy, n = lag_years)) %>%
  ungroup()%>%
  filter(consolidated_lhb == TRUE)
wdf$polyarchy_change <- wdf$v2x_polyarchy_lagged - wdf$v2x_polyarchy
wm <- lm(polyarchy_change ~ v2xnp_client * v2smpolsoc + v2x_polyarchy + e_migdppc, data = wdf)

mimir <- mimir %>% mutate(expected_polyarchy = predict(object = wm, newdata = mimir))
mimir %>% filter(v2smpolsoc %in% c(0.25, 0.75)) %>%
  ggplot(aes(x = v2xnp_client, y = expected_polyarchy, color = as.factor(v2smpolsoc)))+
  geom_line(size = 2.5)+
  scale_color_manual(values = c(client_color, polar_color),
                     labels = c('low', 'high'))+
  theme_minimal()+
  labs(title = 'Clientelism X Polarization',
       subtitle = '  affect democracy 10 years later',
       y = 'Predicted Polyarchy Change',
       x = 'Clientelism',
       color = 'Polarization')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        axis.title.y = element_text(margin = margin(r = 8)),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16),
        legend.title = element_text(size = 18),
        legend.text = element_text(size = 16))
ggsave(filename = "./visuals/model_client_pol_inter.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

Repeat with internal labels
```{r}
mimir %>% filter(v2smpolsoc %in% c(0.25, 0.75)) %>%
  ggplot(aes(x = v2xnp_client, y = expected_polyarchy, color = as.factor(v2smpolsoc)))+
  geom_line(size = 2.5)+
  scale_color_manual(values = c(client_color, polar_color),
                     labels = c('low', 'high'))+
  theme_minimal()+
  labs(title = 'Clientelism X Polarization',
       subtitle = '  affect democracy 10 years later',
       y = 'Predicted Polyarchy Change',
       x = 'Clientelism',
       color = 'Polarization')+
  annotate('text', label = 'low polarization', size = 8, color = client_color, x = 0.625, y = 0.02)+
  annotate('text', label = 'high polarization', size = 8, color = polar_color, x = 0.25, y = -0.15)+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        axis.title.y = element_text(margin = margin(r = 8)),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16),
        legend.position = 'none')
ggsave(filename = "./visuals/model_client_pol_inter_nolegend.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

Chart media fractionalization by polarized society
```{r}
mimir <- data.frame(v2smmefra = rep(point_scale, times = length(point_scale)),
                    v2smpolsoc = rep(point_scale, each = length(point_scale)),
                    v2x_polyarchy = median(vdem_con$v2x_polyarchy[df$v2x_polyarchy >= 0.5], na.rm = TRUE),
                    e_migdppc = median(vdem_con$e_migdppc[df$v2x_polyarchy >= 0.5], na.rm = TRUE))
wdf <- vdem %>%
  group_by(country_name) %>%
  arrange(year) %>%
  mutate(v2x_polyarchy_lagged = lead(v2x_polyarchy, n = lag_years)) %>%
  ungroup()%>%
  filter(consolidated_lhb == TRUE)
wdf$polyarchy_change <- wdf$v2x_polyarchy_lagged - wdf$v2x_polyarchy
wm <- lm(polyarchy_change ~ v2smmefra * v2smpolsoc + v2x_polyarchy + e_migdppc, data = wdf)

mimir <- mimir %>% mutate(expected_polyarchy = predict(object = wm, newdata = mimir))
mimir %>% filter(v2smpolsoc %in% c(0.25, 0.75)) %>%
  ggplot(aes(x = v2smmefra, y = expected_polyarchy, color = as.factor(v2smpolsoc)))+
  geom_line(size = 2.5)+
  scale_color_manual(values = c(media_color, polar_color),
                     labels = c('low', 'high'))+
  theme_minimal()+
  labs(title = 'Fractionalization X Polarization',
       subtitle = '  affect democracy 10 years later',
       y = 'Predicted Polyarchy Change',
       x = 'Fractionalization',
       color = 'Polarization')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        axis.title.y = element_text(margin = margin(r = 8)),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16),
        legend.title = element_text(size = 18),
        legend.text = element_text(size = 16))
ggsave(filename = "./visuals/model_fract_pol_inter.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

Chart polarized society by media fractionalization
```{r}
mimir <- data.frame(v2cacamps = rep(point_scale, times = length(point_scale)),
                     v2smmefra = rep(point_scale, each = length(point_scale)),
                    v2x_polyarchy = median(vdem_con$v2x_polyarchy[df$v2x_polyarchy >= 0.5], na.rm = TRUE),
                    e_migdppc = median(vdem_con$e_migdppc[df$v2x_polyarchy >= 0.5], na.rm = TRUE))
wdf <- vdem %>%
  group_by(country_name) %>%
  arrange(year) %>%
  mutate(v2x_polyarchy_lagged = lead(v2x_polyarchy, n = lag_years)) %>%
  ungroup()%>%
  filter(consolidated_lhb == TRUE)
wdf$polyarchy_change <- wdf$v2x_polyarchy_lagged - wdf$v2x_polyarchy
wm <- lm(polyarchy_change ~ (v2cacamps * v2smmefra) + v2x_polyarchy + e_migdppc, data = wdf)

mimir <- mimir %>% mutate(expected_polyarchy = predict(object = wm, newdata = mimir))
mimir %>% filter(v2smmefra %in% c(0.25, 0.75)) %>%
  ggplot(aes(x = v2cacamps, y = expected_polyarchy, color = as.factor(v2smmefra)))+
  geom_line(size = 2.5)+
  scale_color_manual(values = c(disinfo_color, polar_color),
                     labels = c('low', 'high'))+
  theme_minimal()+
  labs(title = 'Polarization X Fractionalization',
       subtitle = '  affect democracy 10 years later',
       y = 'Predicted Polyarchy Change',
       x = 'Polarization',
       color = 'Fractionalization')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        axis.title.y = element_text(margin = margin(r = 8)),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16),
        legend.title = element_text(size = 18),
        legend.text = element_text(size = 16))
ggsave(filename = "./visuals/model_pol_fract_inter.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

Repeat with internal labels
```{r}
mimir %>% filter(v2smmefra %in% c(0.25, 0.75)) %>%
  ggplot(aes(x = v2cacamps, y = expected_polyarchy, color = as.factor(v2smmefra)))+
  geom_line(size = 2.5)+
  scale_color_manual(values = c(disinfo_color, polar_color),
                     labels = c('low', 'high'))+
  theme_minimal()+
  labs(title = 'Polarization X Fractionalization',
       subtitle = '  affect democracy 10 years later',
       y = 'Predicted Polyarchy Change',
       x = 'Polarization',
       color = 'Fractionalization')+
  annotate('text', label = 'low fractionalization', size = 8, color = disinfo_color, x = 0.625, y = 0.025)+
  annotate('text', label = 'high fractionalization', size = 8, color = polar_color, x = 0.25, y = -0.075)+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        axis.title.y = element_text(margin = margin(r = 8)),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16),
        legend.position = 'none')
ggsave(filename = "./visuals/model_pol_fract_inter_nolegend.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

## Difference in difference charts

Observe polyarchy relative to treatments

dif in dif - clientelism
set level that counts as being "treated" with clientelism
```{r}
clientelism_threshold <- as.numeric(quantile(vdem_con$v2xnp_client, probs = treatment_threshold, na.rm = TRUE))
```

Label years relative to onset of clientelism treatment 
 only count as treatment if happens while inside a democratic spell,
 and if first year of spell did not see high clientelism
 but year count extends ten years prior and after the treatment, 
 regardless of democratic status in those years
```{r}
vdem$year_rel_client <- as.numeric(NA)
vdem$client_control_poly <- as.numeric(NA)
for (i in seq_along(vdem$year)){
  #skip country-years that are not in democratic spells or lack score
  if (is.na(vdem$dem_spell_name[i])) next
  if (is.na(vdem$v2xnp_client[i])) next
  #skip country-years that are in democratic spells that began with high score
  if (vdem$v2xnp_client[!is.na(vdem$dem_spell_name) &
                        vdem$dem_spell_name == vdem$dem_spell_name[i] &
                        !is.na(vdem$dem_spell_running) &
                        vdem$dem_spell_running == 0] > clientelism_threshold) next
  
  #find earliest year within each dem spell that crosses treatment threshold. 
  client_year_zero <- vdem %>% filter(dem_spell_name == vdem$dem_spell_name[i]) %>%
    filter(v2xnp_client >= clientelism_threshold) %>%
    summarize(client_year_zero = min(year, na.rm = TRUE)) %>%
    pull(client_year_zero)
  
  #renumber infinite values as nulls
  #value is Inf if spell never crossed threshold
  client_year_zero <- if_else((client_year_zero == Inf | client_year_zero == -Inf), 
                              as.numeric(NA),
                              client_year_zero)
  
  if (is.na(client_year_zero)) next
  
  #label year of onset as relative year zero
  vdem$year_rel_client[i] <- if_else(vdem$year[i] == client_year_zero,
                                     0,
                                     as.numeric(NA))
}
for (i in seq_along(vdem$year)){
  #locate treatment onset within 10 years of each country-year
  client_year_zero <- vdem %>% 
    filter(country_name == vdem$country_name[i] &
             year >= (vdem$year[i] - 10) &
             year <= (vdem$year[i] + 10) &
             year_rel_client == 0) %>%
    summarize(client_year_zero = min(year)) %>%
    pull(client_year_zero)

  #renumber infinite values as nulls
  #value is Inf if spell never crossed threshold
  client_year_zero <- if_else((client_year_zero == Inf | client_year_zero == -Inf), 
                              as.numeric(NA),
                              client_year_zero)
    
  if (is.na(client_year_zero)) next
  
  #label all preceding and following years in spell, relative to that zero  
  vdem$year_rel_client[i] = vdem$year[i] - client_year_zero
  
  #log control value of clientelism among all consolidated democracies in same absolute year
  vdem$client_control_poly[i] <- if_else(is.na(vdem$year_rel_client[i]),
                                         as.numeric(NA),
                                         mean(vdem$v2x_polyarchy[vdem$v2x_polyarchy >= dem_threshold & 
                                                                   vdem$year == vdem$year[i] &
                                                                   vdem$country_name != vdem$country_name[i]],
                                              na.rm = TRUE))
}
summary(vdem$year_rel_client)
```
```{r}
summary(vdem$client_control_poly)
```

Chart dif in dif - clientelism
```{r}
vdem %>%
  filter(!is.na(year_rel_client)) %>%
  group_by(year_rel_client) %>%
  summarize(polyarchy_client = mean(v2x_polyarchy, na.rm = TRUE),
            polyarchy_control = mean(client_control_poly, na.rm = TRUE)) %>%
  ggplot(aes(x = year_rel_client))+
  geom_point(aes(y = polyarchy_client), color = client_color, size = 4)+
  geom_smooth(data = . %>% filter(year_rel_client < 0),
              method = 'loess',
    aes(y = polyarchy_client), color = client_color, size = 2.5, fill = client_color)+
  geom_smooth(data = . %>% filter(year_rel_client > 0),
              method = 'loess',
              aes(y = polyarchy_client), color = client_color, size = 2.5, fill = client_color)+
  geom_point(aes(y = polyarchy_control), color = dem_color, size = 4)+
  geom_smooth(data = . %>% filter(year_rel_client < 0),
              method = 'loess',
              aes(y = polyarchy_control), color = dem_color, size = 2.5, fill = dem_color)+
  geom_smooth(data = . %>% filter(year_rel_client > 0),
              method = 'loess',
              aes(y = polyarchy_control), color = dem_color, size = 2.5, fill = dem_color)+
  coord_cartesian(xlim = c(-10,10), ylim = c(0,1))+
  geom_vline(xintercept = 0, linetype = 'dashed')+
  annotate('text', label = 'Democracies with\n Clientelism', x = 5, y = 0.375, color = client_color, size = 8)+
  annotate('text', label = 'Other Democracies', x = 5, y = 0.875, color = dem_color, size = 8)+
  theme_minimal()+
  labs(title = 'Onset of Clientelism',
       subtitle = '  effect on democracy',
       y = 'V-Dem Polyarchy Score',
       x = 'Years, Relative to Onset')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16)) 
ggsave(filename = "./visuals/client_dif.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

dif in dif - polarization
set level that counts as being "treated" with polarization
```{r}
polarization_threshold <- as.numeric(quantile(vdem_con$v2cacamps, probs = treatment_threshold, na.rm = TRUE))
```

Label years relative to onset of polarization treatment 
 only count as treatment if happens while inside a democratic spell,
 and if first year of spell did not see high polarization
 but year count extends ten years prior and after the treatment, 
 regardless of democratic status in those years

```{r}
vdem$year_rel_polar <- as.numeric(NA)
vdem$polar_control_poly <- as.numeric(NA)
for (i in seq_along(vdem$year)){
  #skip country-years that are not in democratic spells or lack score
  if (is.na(vdem$dem_spell_name[i])) next
  if (is.na(vdem$v2cacamps[i])) next
  
  #find earliest year within each dem spell that crosses treatment threshold. 
  polar_year_zero <- vdem %>% filter(dem_spell_name == vdem$dem_spell_name[i]) %>%
    filter(v2cacamps >= polarization_threshold) %>%
    summarize(polar_year_zero = min(year, na.rm = TRUE)) %>%
    pull(polar_year_zero)
  
  #skip country-years that are in democratic spells that began with high score
  if (vdem$year[!is.na(vdem$dem_spell_name) &
                vdem$dem_spell_name == vdem$dem_spell_name[i] &
                !is.na(vdem$dem_spell_running) &
                vdem$dem_spell_running == 0] == polar_year_zero) next
  
  #renumber infinite values as nulls
  #value is Inf if spell never crossed threshold
  polar_year_zero <- if_else((polar_year_zero == Inf | polar_year_zero == -Inf), 
                             as.numeric(NA),
                             polar_year_zero)
  
  if (is.na(polar_year_zero)) next
  
  #label year of onset as relative year zero
  vdem$year_rel_polar[i] <- if_else(vdem$year[i] == polar_year_zero,
                                    0,
                                    as.numeric(NA))
}
for (i in seq_along(vdem$year)){
  #locate treatment onset within 10 years of each country-year
  polar_year_zero <- vdem %>% 
    filter(country_name == vdem$country_name[i] &
             year >= (vdem$year[i] - 10) &
             year <= (vdem$year[i] + 10) &
             year_rel_polar == 0) %>%
    summarize(polar_year_zero = min(year)) %>%
    pull(polar_year_zero)
  
  #renumber infinite values as nulls
  #value is Inf if spell never crossed threshold
  polar_year_zero <- if_else((polar_year_zero == Inf | polar_year_zero == -Inf), 
                             as.numeric(NA),
                             polar_year_zero)
  
  if (is.na(polar_year_zero)) next
  
  #label all preceding and following years in spell, relative to that zero  
  vdem$year_rel_polar[i] = vdem$year[i] - polar_year_zero
  
  #log control value of polarization among all consolidated democracies in same absolute year
  vdem$polar_control_poly[i] <- if_else(is.na(vdem$year_rel_polar[i]),
                                        as.numeric(NA),
                                        mean(vdem$v2x_polyarchy[vdem$v2x_polyarchy >= dem_threshold & 
                                                                  vdem$year == vdem$year[i] &
                                                                  vdem$country_name != vdem$country_name[i]],
                                             na.rm = TRUE))
}
summary(vdem$year_rel_polar)
summary(vdem$polar_control_poly)
```

Chart dif in dif - polarization
```{r}
vdem %>%
  filter(!is.na(year_rel_polar)) %>%
  group_by(year_rel_polar) %>%
  summarize(polyarchy_polar = mean(v2x_polyarchy, na.rm = TRUE),
            polyarchy_control = mean(polar_control_poly, na.rm = TRUE)) %>%
  ggplot(aes(x = year_rel_polar))+
  geom_point(aes(y = polyarchy_polar), color = polar_color, size = 4)+
  geom_smooth(data = . %>% filter(year_rel_polar < 0),
              method = 'loess',
              aes(y = polyarchy_polar), color = polar_color, size = 2.5, fill = polar_color)+
  geom_smooth(data = . %>% filter(year_rel_polar > 0),
              method = 'loess',
              aes(y = polyarchy_polar), color = polar_color, size = 2.5, fill = polar_color)+
  geom_point(aes(y = polyarchy_control), color = dem_color, size = 4)+
  geom_smooth(data = . %>% filter(year_rel_polar < 0),
              method = 'loess',
              aes(y = polyarchy_control), color = dem_color, size = 2.5, fill = dem_color)+
  geom_smooth(data = . %>% filter(year_rel_polar > 0),
              method = 'loess',
              aes(y = polyarchy_control), color = dem_color, size = 2.5, fill = dem_color)+
  coord_cartesian(xlim = c(-10,10), ylim = c(0,1))+
  geom_vline(xintercept = 0, linetype = 'dashed')+
  annotate('text', label = 'Democracies with\n Polarization', x = 5, y = 0.375, color = polar_color, size = 8)+
  annotate('text', label = 'Other Democracies', x = 5, y = 0.875, color = dem_color, size = 8)+
  theme_minimal()+
  labs(title = 'Onset of Polarization',
       subtitle = '  effect on democracy',
       y = 'V-Dem Polyarchy Score',
       x = 'Years, Relative to Onset')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16)) 
ggsave(filename = "./visuals/polar_dif.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

dif in dif - party disinfo

Set level that counts as being "treated" with par_disinfo
```{r}
par_disinfo_threshold <- as.numeric(quantile(vdem_con$v2smpardom, probs = treatment_threshold, na.rm = TRUE))
```

Label years relative to onset of party disinfo treatment 
 only count as treatment if happens while inside a democratic spell,
 and if first year of spell did not see high par_disinfo
 but year count extends ten years prior and after the treatment, 
 regardless of democratic status in those years
```{r}
vdem$year_rel_par_disinfo <- as.numeric(NA)
vdem$par_disinfo_control_poly <- as.numeric(NA)
for (i in seq_along(vdem$year)){
  #skip country-years that are not in democratic spells or lack score
  if (is.na(vdem$dem_spell_name[i])) next
  if (is.na(vdem$v2smpardom[i])) next
  
  #find earliest year within each dem spell that crosses treatment threshold. 
  par_disinfo_year_zero <- vdem %>% filter(dem_spell_name == vdem$dem_spell_name[i]) %>%
    filter(v2smpardom >= par_disinfo_threshold) %>%
    summarize(par_disinfo_year_zero = min(year, na.rm = TRUE)) %>%
    pull(par_disinfo_year_zero)
  
  #skip country-years that are in democratic spells that began with high score
  if (vdem$year[!is.na(vdem$dem_spell_name) &
                vdem$dem_spell_name == vdem$dem_spell_name[i] &
                !is.na(vdem$dem_spell_running) &
                vdem$dem_spell_running == 0] == par_disinfo_year_zero) next
  
  #renumber infinite values as nulls
  #value is Inf if spell never crossed threshold
  par_disinfo_year_zero <- if_else((par_disinfo_year_zero == Inf | par_disinfo_year_zero == -Inf), 
                                   as.numeric(NA),
                                   par_disinfo_year_zero)
  
  if (is.na(par_disinfo_year_zero)) next
  
  #label year of onset as relative year zero
  vdem$year_rel_par_disinfo[i] <- if_else(vdem$year[i] == par_disinfo_year_zero,
                                          0,
                                          as.numeric(NA))
}
for (i in seq_along(vdem$year)){
  #locate treatment onset within 10 years of each country-year
  par_disinfo_year_zero <- vdem %>% 
    filter(country_name == vdem$country_name[i] &
             year >= (vdem$year[i] - 10) &
             year <= (vdem$year[i] + 10) &
             year_rel_par_disinfo == 0) %>%
    summarize(par_disinfo_year_zero = min(year)) %>%
    pull(par_disinfo_year_zero)
  
  #renumber infinite values as nulls
  #value is Inf if spell never crossed threshold
  par_disinfo_year_zero <- if_else((par_disinfo_year_zero == Inf | par_disinfo_year_zero == -Inf), 
                                   as.numeric(NA),
                                   par_disinfo_year_zero)
  
  if (is.na(par_disinfo_year_zero)) next
  
  #label all preceding and following years in spell, relative to that zero  
  vdem$year_rel_par_disinfo[i] = vdem$year[i] - par_disinfo_year_zero
  
  #log control value of par_disinfo among all consolidated democracies in same absolute year
  vdem$par_disinfo_control_poly[i] <- if_else(is.na(vdem$year_rel_par_disinfo[i]),
                                              as.numeric(NA),
                                              mean(vdem$v2x_polyarchy[vdem$v2x_polyarchy >= dem_threshold & 
                                                                        vdem$year == vdem$year[i] &
                                                                        vdem$country_name != vdem$country_name[i]],
                                                   na.rm = TRUE))
}
summary(vdem$year_rel_par_disinfo)
summary(vdem$par_disinfo_control_poly)
```

Chart dif in dif - disinfo
```{r}
vdem %>%
  filter(!is.na(year_rel_par_disinfo)) %>%
  group_by(year_rel_par_disinfo) %>%
  summarize(polyarchy_par_disinfo = mean(v2x_polyarchy, na.rm = TRUE),
            polyarchy_control = mean(par_disinfo_control_poly, na.rm = TRUE)) %>%
  ggplot(aes(x = year_rel_par_disinfo))+
  geom_point(aes(y = polyarchy_par_disinfo), color = disinfo_color, size = 4)+
  geom_smooth(data = . %>% filter(year_rel_par_disinfo < 0),
              method = 'loess',
              aes(y = polyarchy_par_disinfo), color = disinfo_color, size = 2.5, fill = disinfo_color)+
  geom_smooth(data = . %>% filter(year_rel_par_disinfo > 0),
              method = 'loess',
              aes(y = polyarchy_par_disinfo), color = disinfo_color, size = 2.5, fill = disinfo_color)+
  geom_point(aes(y = polyarchy_control), color = dem_color, size = 4)+
  geom_smooth(data = . %>% filter(year_rel_par_disinfo < 0),
              method = 'loess',
              aes(y = polyarchy_control), color = dem_color, size = 2.5, fill = dem_color)+
  geom_smooth(data = . %>% filter(year_rel_par_disinfo > 0),
              method = 'loess',
              aes(y = polyarchy_control), color = dem_color, size = 2.5, fill = dem_color)+
  coord_cartesian(xlim = c(-10,10), ylim = c(0,1))+
  geom_vline(xintercept = 0, linetype = 'dashed')+
  annotate('text', label = 'Democracies with\n Disinformation', x = 5, y = 0.375, color = disinfo_color, size = 8)+
  annotate('text', label = 'Other Democracies', x = 5, y = 0.875, color = dem_color, size = 8)+
  theme_minimal()+
  labs(title = 'Onset of Disinformation from Parties',
       subtitle = '  effect on democracy',
       y = 'V-Dem Polyarchy Score',
       x = 'Years, Relative to Onset')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16)) 
ggsave(filename = "./visuals/par_disinfo_dif.jpg",
       width = 10,
       height = 6,
       units = 'in')

```

dif in dif - online consumption X fractionalization

Set level that counts as being "treated" with frac_inter
```{r}
frac_inter_threshold <- as.numeric(quantile(vdem_con$smonexXsmmefra, probs = treatment_threshold, na.rm = TRUE))
```

Label years relative to onset of frac_inter treatment 
 only count as treatment if happens while inside a democratic spell,
 and if first year of spell did not see high frac_inter
 but year count extends ten years prior and after the treatment, 
 regardless of democratic status in those years
```{r}
vdem$year_rel_frac_inter <- as.numeric(NA)
vdem$frac_inter_control_poly <- as.numeric(NA)
for (i in seq_along(vdem$year)){
  #skip country-years that are not in democratic spells or lack score
  if (is.na(vdem$dem_spell_name[i])) next
  if (is.na(vdem$smonexXsmmefra[i])) next
  
  #find earliest year within each dem spell that crosses treatment threshold. 
  frac_inter_year_zero <- vdem %>% filter(dem_spell_name == vdem$dem_spell_name[i]) %>%
    filter(smonexXsmmefra >= frac_inter_threshold) %>%
    summarize(frac_inter_year_zero = min(year, na.rm = TRUE)) %>%
    pull(frac_inter_year_zero)
  
  #skip country-years that are in democratic spells that began with high score
  if (vdem$year[!is.na(vdem$dem_spell_name) &
                vdem$dem_spell_name == vdem$dem_spell_name[i] &
                !is.na(vdem$dem_spell_running) &
                vdem$dem_spell_running == 0] == frac_inter_year_zero) next
  
  #renumber infinite values as nulls
  #value is Inf if spell never crossed threshold
  frac_inter_year_zero <- if_else((frac_inter_year_zero == Inf | frac_inter_year_zero == -Inf), 
                                  as.numeric(NA),
                                  frac_inter_year_zero)
  
  if (is.na(frac_inter_year_zero)) next
  
  #label year of onset as relative year zero
  vdem$year_rel_frac_inter[i] <- if_else(vdem$year[i] == frac_inter_year_zero,
                                         0,
                                         as.numeric(NA))
}
for (i in seq_along(vdem$year)){
  #locate treatment onset within 10 years of each country-year
  frac_inter_year_zero <- vdem %>% 
    filter(country_name == vdem$country_name[i] &
             year >= (vdem$year[i] - 10) &
             year <= (vdem$year[i] + 10) &
             year_rel_frac_inter == 0) %>%
    summarize(frac_inter_year_zero = min(year)) %>%
    pull(frac_inter_year_zero)
  
  #renumber infinite values as nulls
  #value is Inf if spell never crossed threshold
  frac_inter_year_zero <- if_else((frac_inter_year_zero == Inf | frac_inter_year_zero == -Inf), 
                                  as.numeric(NA),
                                  frac_inter_year_zero)
  
  if (is.na(frac_inter_year_zero)) next
  
  #label all preceding and following years in spell, relative to that zero  
  vdem$year_rel_frac_inter[i] = vdem$year[i] - frac_inter_year_zero
  
  #log control value of frac_inter among all consolidated democracies in same absolute year
  vdem$frac_inter_control_poly[i] <- if_else(is.na(vdem$year_rel_frac_inter[i]),
                                             as.numeric(NA),
                                             mean(vdem$v2x_polyarchy[vdem$v2x_polyarchy >= dem_threshold & 
                                                                       vdem$year == vdem$year[i] &
                                                                       vdem$country_name != vdem$country_name[i]],
                                                  na.rm = TRUE))
}
summary(vdem$year_rel_frac_inter)
summary(vdem$frac_inter_control_poly)
```

Chart dif in dif - online consumption times fractionalization
```{r}
vdem %>%
  filter(!is.na(year_rel_frac_inter)) %>%
  group_by(year_rel_frac_inter) %>%
  summarize(polyarchy_frac_inter = mean(v2x_polyarchy, na.rm = TRUE),
            polyarchy_control = mean(frac_inter_control_poly, na.rm = TRUE)) %>%
  ggplot(aes(x = year_rel_frac_inter))+
  geom_point(aes(y = polyarchy_frac_inter), color = media_color, size = 4)+
  geom_smooth(data = . %>% filter(year_rel_frac_inter < 0),
              method = 'loess',
              aes(y = polyarchy_frac_inter), color = media_color, size = 2.5, fill = media_color)+
  geom_smooth(data = . %>% filter(year_rel_frac_inter > 0),
              method = 'loess',
              aes(y = polyarchy_frac_inter), color = media_color, size = 2.5, fill = media_color)+
  geom_point(aes(y = polyarchy_control), color = dem_color, size = 4)+
  geom_smooth(data = . %>% filter(year_rel_frac_inter < 0),
              method = 'loess',
              aes(y = polyarchy_control), color = dem_color, size = 2.5, fill = dem_color)+
  geom_smooth(data = . %>% filter(year_rel_frac_inter > 0),
              method = 'loess',
              aes(y = polyarchy_control), color = dem_color, size = 2.5, fill = dem_color)+
  coord_cartesian(xlim = c(-10,10), ylim = c(0,1))+
  geom_vline(xintercept = 0, linetype = 'dashed')+
  annotate('text', label = 'Democracies with\n Online\n Fractionalism', x = 5, y = 0.375, color = media_color, size = 8)+
  annotate('text', label = 'Other Democracies', x = 5, y = 0.875, color = dem_color, size = 8)+
  theme_minimal()+
  labs(title = 'Onset of Online Consumpton and Fractionalism',
       subtitle = '  effect on democracy',
       y = 'V-Dem Polyarchy Score',
       x = 'Years, Relative to Onset')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18, face = 'bold'),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16)) 
ggsave(filename = "./visuals/media_dif.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

# Charts for country case studies 

Check GDP per capita to ensure comparability
```{r}
vdem %>% filter(year == 1995,
                country_name %in% c('Venezuela', 'Brazil', 'Uruguay', 'Hungary', 'Poland', 'Estonia')) %>%
  select(country_name, e_migdppc)
```

Write generic code for country plots
```{r}
plot_case <- function(country_case){
  max_year <- max(vdem$year, na.rm = TRUE)
  case_labels_df <- data.frame(variable = c('Democracy', 'Clientelism', 'Polarization', 'Disinformation'),
                               last_value = c(vdem$v2x_polyarchy[vdem$year == max_year &
                                                                   vdem$country_name == country_case],
                                              vdem$v2xnp_client[vdem$year == max_year&
                                                                  vdem$country_name == country_case],
                                              vdem$v2cacamps[vdem$year == max_year&
                                                               vdem$country_name == country_case],
                                              vdem$v2smonex[vdem$year == max_year&
                                                              vdem$country_name == country_case] *
                                                vdem$v2smpardom[vdem$year == max_year&
                                                                  vdem$country_name == country_case]),
                               color = c(dem_color, client_color, polar_color, disinfo_color))
  
  ggplot(data = (vdem %>% filter(country_name == country_case &
                                   year >= 1981)),
         aes(x = year))+
    geom_line(aes(y = v2x_polyarchy), color = dem_color, size = 2.5)+
    geom_line(aes(y = v2xnp_client), color = client_color, size = 2.5, linetype = 'dotted')+
    geom_line(aes(y = v2cacamps), color = polar_color, size = 2.5, linetype = 'twodash')+
    geom_line(aes(y = (v2smonex * v2smpardom)), color = disinfo_color, size = 2.5, linetype = 'dashed')+
    coord_cartesian(xlim = c(1980, 2020), ylim = c(0,1))+
    scale_y_continuous(sec.axis = dup_axis(
      breaks = case_labels_df$last_value,
      labels = case_labels_df$variable))+
    theme_minimal()+
    labs(title = paste0(country_case, "'s History"),
         subtitle  = " of Democracy and its Solvents")+
    theme(title = element_text(size = 20, face = 'bold'),
          axis.title = element_blank(),
          panel.grid.minor = element_blank(),
          axis.text = element_text(size = 16),
          axis.text.y.right = element_text(size = 16, color = c(dem_color, client_color, polar_color, disinfo_color))) 
}

```

Apply to desired cases

```{r}
plot_case(country_case = 'Venezuela')
ggsave(filename = "./visuals/case_venezuela.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

```{r}
plot_case(country_case = 'Brazil')
ggsave(filename = "./visuals/case_brazil.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

```{r}
plot_case(country_case = 'Uruguay')
ggsave(filename = "./visuals/case_uruguay.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

```{r}
plot_case(country_case = 'Hungary')
ggsave(filename = "./visuals/case_hungary.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

```{r}
plot_case(country_case = 'Poland')
ggsave(filename = "./visuals/case_poland.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

```{r}
plot_case(country_case = 'Estonia')+
  scale_x_continuous(limits = c(1992, 2020))
ggsave(filename = "./visuals/case_estonia.jpg",
       width = 10,
       height = 6,
       units = 'in')
```

Verify claim about low distinctiveness of party platforms in Brazil
```{r}
vdem %>% filter(country_name == 'Venezuela', year >= 1950) %>%
  ggplot(aes(x = year, y = v2psplats))+
  geom_line(color = polar_color, size = 2.5)+
  theme_minimal()+
  coord_cartesian(ylim = c(0,1))+
  labs(title = 'Party Platforms Indistinct in Venezuela',
       y = 'Differentiation of Party Platforms',
       x = '')+
  theme(title = element_text(size = 20, face = 'bold'),
        axis.title = element_text(size = 18),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16),
        axis.title.y = element_text(margin = margin(r = 8)))

```


